---
title: "Assignment 5 - Meta-analysis of pitch in schizophrenia"
author: "Malte, Oliver, Anna & Louise"
date: "November, 2019"
output:   
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
p_load(tidyverse)
```

# Building on the shoulders of giants: meta-analysis

## Questions to be answered

1. What is the current evidence for distinctive vocal patterns in schizophrenia? Report how many papers report quantitative estimates, comment on what percentage of the overall studies reviewed they represent (see PRISMA chart) your method to analyze them, the estimated effect size of the difference (mean effect size and standard error) and forest plots representing it. N.B. Only measures of pitch mean and pitch sd are required for the assignment. Feel free to ignore the rest (although pause behavior looks interesting, if you check my article).

2. Do the results match your own analysis from Assignment 3? If you add your results to the meta-analysis, do the estimated effect sizes change? Report the new estimates and the new forest plots.

3. Assess the quality of the literature: report and comment on heterogeneity of the studies (tau, I2), on publication bias (funnel plot), and on influential studies.

## Tips on the process to follow:

- Download the data on all published articles analyzing voice in schizophrenia and the prisma chart as reference of all articles found and reviewed
```{r}
data <- readxl::read_xlsx("Matrix_MetaAnalysis_Diagnosis_updated290719.xlsx")
```
- Look through the dataset to find out which columns to use, and if there is any additional information written as comments (real world data is always messy!).
    * Hint: PITCH_F0M and PITCH_F0SD group of variables are what you need
    * Hint: Make sure you read the comments in the columns: `pitch_f0_variability`, `frequency`, `Title`,  `ACOUST_ANA_DESCR`, `DESCRIPTION`, and `COMMENTS`
```{r}
df <- subset(data[,c(1:2, 4, 21, 22, 69, 70, 71, 72, 73, 103, 104:107)])
```
- Following the procedure in the slides calculate effect size and variability of the effect size per each study. N.B. we focus on pitch mean and pitch standard deviation.
```{r}
p_load(metafor)

# Calculating effect size
PitchMeanES <- escalc('SMD',
             n1i = SAMPLE_SIZE_SZ, n2i = SAMPLE_SIZE_HC,
             m1i = PITCH_F0_SZ_M, m2i = PITCH_F0_HC_M,
             sd1i = PITCH_F0_SZ_SD, sd2i = PITCH_F0_HC_SD,
             data = df)

PitchSDES <- escalc('SMD',
                    n1i = SAMPLE_SIZE_SZ, n2i = SAMPLE_SIZE_HC,
                    m1i = PITCH_F0SD_SZ_M, m2i = PITCH_F0SD_HC_M,
                    sd1i = PITCH_F0SD_SZ_SD, sd2i = PITCH_F0SD_HC_SD,
                    data = df)

``` 

 . first try using lmer (to connect to what you know of mixed effects models)

```{r}
p_load(lmerTest)

mean_m1 <- lmer(yi ~ 1 + (1|StudyID), PitchMeanES, weights = 1/vi, # The bigger the variance, the smaller the decimal
                 REML = F,
                 control = lmerControl(
                     check.nobs.vs.nlev = "ignore",
                     check.nobs.vs.nRE = "ignore"))
summary(mean_m1)

sd_m1 <- lmer(yi ~ 1 + (1|StudyID), PitchSDES, weights = 1/vi, # The bigger the variance, the smaller the decimal
                 REML = F,
                 control = lmerControl(
                     check.nobs.vs.nlev = "ignore",
                     check.nobs.vs.nRE = "ignore"))
summary(sd_m1)
# error: boundary (singular) fit: see ?isSingular

```

 . then use rma() (to get some juicy additional statistics)
 
```{r}
mean_m2 <- rma(yi, vi, data = PitchMeanES, slab = StudyID)
summary(mean_m2)

sd_m2 <- rma(yi, vi, data = PitchSDES, slab = StudyID)
sd_m2
```
 
- Build a forest plot of the results (forest(model))

```{r}
forest(mean_m2)

forest(sd_m2)
```

- Go back to Assignment 3, add your own study to the data table, and re-run meta-analysis. Do the results change?
```{r}
# Loading the pitch data
pitch_data <- read_csv("pitch_data.csv")

# Creating df for controls
pitch_data_hc <- filter(pitch_data, Diagnosis == 0)

# Creating df for SCZ
pitch_data_sz <- filter(pitch_data, Diagnosis == 1)

# Binding the dfs together
# pitch_data2 <- rbind(pitch_data_hc, pitch_data_sz)


# Now we make another column called unique_ID - so we can count how many HCs and SCZs there are
pitch_data$unique_ID <- paste(pitch_data$Participant, pitch_data$Study, sep = "_")
pitch_data$unique_ID <- as.factor(pitch_data$unique_ID)
unique(pitch_data$unique_ID)
# = 204 in total

pitch_data_hc$unique_ID <- paste(pitch_data_hc$Participant, pitch_data_hc$Study, sep = "_")
pitch_data_hc$unique_ID <- as.factor(pitch_data_hc$unique_ID)
unique(pitch_data_hc$unique_ID)
# HC = 173

204-173
# 31 are scz

# Make dataframe with the columns we need
own_study <- data.frame(StudyID = 69, # høhø
                        SAMPLE_SIZE_HC = 173, 
                        SAMPLE_SIZE_SZ = 31, 
                        PITCH_F0_HC_M = mean(pitch_data_hc$Mean), 
                        PITCH_F0_SZ_M = mean(pitch_data_sz$Mean), 
                        PITCH_F0_HC_SD = sd(pitch_data_hc$Mean), 
                        PITCH_F0_SZ_SD = sd(pitch_data_sz$Mean))

own_study_2 <- data.frame(StudyID = 69,
                        SAMPLE_SIZE_HC = 173, 
                        SAMPLE_SIZE_SZ = 31, 
                        PITCH_F0SD_HC_M = mean(pitch_data_hc$SD), 
                        PITCH_F0SD_SZ_M = mean(pitch_data_sz$SD), 
                        PITCH_F0SD_HC_SD = sd(pitch_data_hc$SD), 
                        PITCH_F0SD_SZ_SD = sd(pitch_data_sz$SD))

# Now we want to bind our own study together with the rest of the studies

# Selecting only the relevant variables (the ones used in escalc earlier)
PitchMeanES_select <- select(PitchMeanES, StudyID, SAMPLE_SIZE_HC, SAMPLE_SIZE_SZ, PITCH_F0_HC_M, PITCH_F0_SZ_M, PITCH_F0_HC_SD, PITCH_F0_HC_SD, PITCH_F0_SZ_SD)

PitchSDES_select <- select(PitchSDES, StudyID, SAMPLE_SIZE_HC, SAMPLE_SIZE_SZ, PITCH_F0SD_HC_M, PITCH_F0SD_SZ_M, PITCH_F0SD_HC_SD, PITCH_F0SD_SZ_SD)

# Binding the dataset with our study
PitchMeanES_all <- dplyr::bind_rows(PitchMeanES_select, own_study)
PitchSDES_all <- dplyr::bind_rows(PitchSDES_select, own_study_2)
PitchMeanES_all$StudyID<-as.factor(PitchMeanES_all$StudyID)
PitchSDES_all$StudyID <-as.factor(PitchSDES_all$StudyID)

# Calculting effect effect size for pitch mean and pitch variability for each study (pretty much a duplicate of first escalc except new data)

# First the mean stuff
PitchMeanES_calc <- escalc("SMD",
                           n1i = SAMPLE_SIZE_SZ, n2i = SAMPLE_SIZE_HC,
                           m1i = PITCH_F0_SZ_M, m2i = PITCH_F0_HC_M,
                           sd1i = PITCH_F0_SZ_SD, sd2i = PITCH_F0_HC_SD,
                           data = PitchMeanES_all)

# Then the SD stuff
PitchSDES_calc <- escalc("SMD",
                         n1i = SAMPLE_SIZE_SZ, n2i = SAMPLE_SIZE_HC,
                         m1i = PITCH_F0SD_SZ_M, m2i = PITCH_F0SD_HC_M,
                         sd1i = PITCH_F0SD_SZ_SD, sd2i = PITCH_F0SD_HC_SD,
                         data = PitchSDES_all)

# Running models
all_mean_m1 <- lmer(yi ~ 1 + (1|StudyID), PitchMeanES_calc, weights = 1/vi, # The bigger the variance, the smaller the decimal
                 REML = F,
                 control = lmerControl(
                     check.nobs.vs.nlev = "ignore",
                     check.nobs.vs.nRE = "ignore"))
summary(all_mean_m1)

all_sd_m1 <- lmer(yi ~ 1 + (1|StudyID), PitchSDES_calc, weights = 1/vi, # The bigger the variance, the smaller the decimal
                 REML = F,
                 control = lmerControl(
                     check.nobs.vs.nlev = "ignore",
                     check.nobs.vs.nRE = "ignore"))
summary(all_sd_m1)
# error: boundary (singular) fit: see ?isSingular

## SO!!  does the effect size change by including our study?
# Now rma models

# Mean
all_mean_m2 <- rma(yi, vi, data = PitchMeanES_calc, slab = StudyID)
summary(all_mean_m2)
forest(all_mean_m2)

# The influence stuff from Riccardo:
inf_mean <- influence(all_mean_m2)
print(inf)
plot(inf)

# SD
all_sd_m2 <- rma(yi, vi, data = PitchSDES_calc, slab = StudyID)
summary(all_sd_m2)
forest(all_sd_m2)

# Influence stuff:
inf_sd <- influence(all_sd_m2)
print(inf_sd)
plot(inf_sd)
```


- Now look at the output of rma() and check tau and I2
